Boutiques: a flexible framework for automated application integration in computing platforms

### 2017-11-02 boutiquespaper.tex
A paragraph on Nipype

CBRAIN~\cite{SHER-14} is a web platform that can process data
distributed into multiple storage locations on computing clusters and
clouds. CBRAIN offers transparent access to remote data sources,
distributed computing sites, and an array of processing and
visualization tools within a controlled, secure environment.  The
CBRAIN service deployed at the Montreal Neurological Institute relies
on the infrastructure provided by Compute Canada~\cite{das2016mni}. It
currently provides 500+ collaborators in 22 countries with web access
to several systems, including 6 clusters of the Compute Canada
high-performance computing infrastructure (totaling more than 100,000
computing cores and 40PB of disk storage) and Amazon EC2. CBRAIN
transiently stores about 10 million files representing over 50TB
distributed in 42 servers. 51 public data processing applications are
integrated and over 340,000 processing batches have been submitted since 2010.

@@

>>>>

CBRAIN (\url{http://cbrain.mcgill.ca}) ~\cite{SHER-14} is a web
platform that can process data distributed into multiple storage
locations on computing clusters and clouds. CBRAIN offers transparent
access to remote data sources, distributed computing sites, and an
array of processing and visualization tools within a controlled,
secure environment.  The CBRAIN service deployed at the Montreal
Neurological Institute relies on the infrastructure provided by
Compute Canada~\cite{das2016mni}. It currently provides 500+
collaborators in 22 countries with web access to several systems,
including 6 clusters of the Compute Canada high-performance computing
infrastructure (totaling more than 100,000 computing cores and 40PB of
disk storage) and Amazon EC2. CBRAIN transiently stores about 10
million files representing over 50TB distributed in 42 servers. 51
public data processing applications are integrated and over 340,000
processing batches have been submitted since 2010.

@@

\subsubsection{Nipype}
Nipype (\url{http://nipype.readthedocs.io/en/latest/})~\cite{gorgolewski2011nipype} is a workflow engine widely used in
neuroinformatics. Nipype workflows can be composed from \boutiques
tools using the Python API. As an example, we implemented NipBIDS, a
Nipype workflow to process BIDS datasets using BIDS apps. NipBIDS
iterates participant analyses on all the subjects found in a BIDS
dataset and runs a group analysis if requested. It is available at
\url{https://github.com/big-data-lab-team/sim/tree/master/sim/other_wf_examples/nipype}.
